Paper_analyses

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
1

@@

  db_full4new_stim_screen_pupil_nopract %>%
    subset(ssid < 500)%>%
  # subset(Group == "NT")%>%
  group_by(ssid, Group)%>%
  mutate(cor_ar_pup = cor(arousal, pup_basCor, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS,cor_ar_pup, color = Group))+
  geom_point()+
    geom_smooth(method = lm, se = F)+
    ggpubr::stat_cor()
  geom_hline(yintercept = -.75)+
  geom_hline(yintercept = -.90)

@@

# fit pupil response froma rousal and valence
pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))

@@

plots_paper$interaction_ar_vl
```

@@

```{r}
# with arousal as DV
pupil_arousal_findings$arousal_from_pup <- lmer(arousal_c ~ valence_c*pup_basCor  + (1| stimIAPS)+
                                                 # (1 | ssid),
                                                  (0 +valence_c+pup_basCor | ssid),
                                                REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))
summary(pupil_arousal_findings$arousal_from_pup)

@@

pupil_arousal_findings$valence_from_pup <- lmer(valence_c ~ arousal_c*pup_basCor  + (1| stimIAPS)+
                                                 # (1 | ssid),
                                                  (0 +arousal_c +pup_basCor | ssid),
                                                REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num<500 & 
                                      arousal_outler == FALSE))
summary(pupil_arousal_findings$valence_from_pup)
anova(pupil_arousal_findings$valence_from_pup)

@@

# new folks 
library(readr)
tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")
View(tmp_df4_timeseries_345_356)

@@

# match types of merging variables
tmp.df4_full_stim_downs_jun2021_with_beh2$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)
db_full4new_stim_subset$ssid<- as.character(db_full4new_stim_subset$ssid)

@@

# temp backup
tmp.df4_full_stim_downs_jun2021_backup<- tmp.df4_full_stim_downs_jun2021
tmp_df4_timeseries_345_356_stim_downs_backup<- tmp_df4_timeseries_345_356_stim_downs

@@

# bind old and new data
tmp.df4_full_stim_downs_jun2021 <- bind_rows(tmp.df4_full_stim_downs_jun2021,tmp_df4_timeseries_345_356_stim_downs)

tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)
db_full4new_stim_subset$tNo<- as.character(db_full4new_stim_subset$tNo)

# backup[]
tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_60bins

tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021, db_full4new_stim_subset, by = c("ssid", "tNo", "trial"))

@@

tmp.df4_full_stim_downs_jun2021_60bins$Label<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,8)

tmp.df4_full_stim_downs_jun2021_60bins$Label2<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,4)
imageJ_IAPS$Label2<- substr(imageJ_IAPS$Label, 1,4)

unique(imageJ_IAPS$Label2)
unique(tmp.df4_full_stim_downs_jun2021_60bins$Label2)

# backup
tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_60bins

tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_60bins, imageJ_IAPS, by = "Label2")

@@

Quick check that things make sense
30 s timebins
```{r eval=FALSE, include=FALSE}
unique(tmp.df4_full_stim_downs_jun2021_with_beh$timebin2)
# group_by(stimIAPS)%>%
tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample >= 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

# higher sample rate]

@@

ground_arousal_lab

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

@@

@@

timecourse_60bin_result_df %>%
  ggplot(aes(timebins, Estimate_ar_vl))+
  geom_line(size = 1)
  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
  geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
  geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")

@@

timecourse_60bin_result_df %>%
  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  subset(ssid == 331 & tNo ==40)%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))%>%
   ggplot(aes(timerezero3, pup_velocity))+
  geom_line()+
  geom_line(aes(y = pup_vel_smooth), color = 'red')

@@

paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2)

@@

pupiul velocity and speed might better caprure arousal dynamics because the temporal dynamics are less adffected by a susrtauned effect of brighetenss. whereas amplitude is p[robably strongly affected by brighteness which restricts variability in input from a arousal componenets

>>>>

# behavioural data
db_345_355
db_f

@@

  db_full4new_stim_screen_pupil_nopract$screencontent

  table(is.na(  db_full4new_stim_screen_pupil_nopract$pup_basCor ))
  unique(  db_full4new_stim_screen_pupil_nopract$ssid)

  db_full4new_stim_screen_pupil_nopract %>%
    # subset(ssid_num < 343)%>%
  # subset(Group == "NT")%>%
  group_by(ssid)%>%
  mutate(cor_ar_pup = cor(arousal, pup_basCor, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS,cor_ar_pup))+
  geom_point()+
    geom_smooth(method = lm, se = F)+
    ggpubr::stat_cor()
  geom_hline(yintercept = -.75)+
  geom_hline(yintercept = -.90)

@@

# fit pupil response froma rousal and valence

table(is.na(db_full4new_stim_screen_pupil_nopract$valence_c))
pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))

@@

db_full4new_stim_screen_pupil_nopract_nt<- subset(db_full4new_stim_screen_pupil_nopract, Group == "NT")

db_full4new_stim_screen_pupil_nopract_nt%>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, valence_c))+
  geom_point()+
  ggpubr::stat_cor()

cor.test(db_full4new_stim_screen_pupil_nopract_nt$valence, db_full4new_stim_screen_pupil_nopract_nt$arousal_c)
car::scatter3d(db_full4new_stim_screen_pupil_nopract_nt$arousal_c, 
          db_full4new_stim_screen_pupil_nopract_nt$pup_basCor, 
          db_full4new_stim_screen_pupil_nopract_nt$valence_c,
          fit = "smooth"
          # point = FALSE,

          # surface = FALSE,
          # point.col = ""
          )
```

quick check of TAS

db_full4new_stim_screen_pupil_nopract$TASc<- scale(db_full4new_stim_screen_pupil_nopract$TAS, center = TRUE, scale = TRUE)[,1]

pupil_arousal_findings$pupil_from_ar_vale_TAS <- lmer(pup_basCor ~ (valence_c* arousal_c)*TASc +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ arousal_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT"))
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_vale_TAS)

interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale_TAS, pred = TASc, modx = arousal_c)
interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale_TAS, pred = TASc, modx = arousal_c, mod2= valence_c)

@@

```{r}
# with arousal as DV
pupil_arousal_findings$arousal_from_pup <- lmer(arousal ~ valence_c*pup_basCor  + 
                                                  (1| stimIAPS)+
                                                 # (1 | stimIAPS)+
                                                  (1  | ssid),
                                                REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))
summary(pupil_arousal_findings$arousal_from_pup)

@@

pupil_arousal_findings$valence_from_pup <- lmer(valence ~ arousal_c*pup_basCor  + (1| stimIAPS)+
                                                 # (1 | ssid),
                                                  (0 +arousal_c | ssid),
                                                REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    Group == "NT"))
summary(pupil_arousal_findings$valence_from_pup)
anova(pupil_arousal_findings$valence_from_pup)

@@

unique(tmp.df4_full_stim_downs_jun2021$timebin)
# new folks 
library(readr)

tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")
View(tmp_df4_timeseries_345_356)

@@

# match types of merging variables (this is 30-hz)

unique(tmp.df4_full_stim_downs_jun2021_with_beh2$timebin2)

unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2)
tmp.df4_full_stim_downs_jun2021_with_beh2$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)
db_full4new_stim_subset$ssid<- as.character(db_full4new_stim_subset$ssid)

@@

# temp backup

tmp.df4_full_stim_downs_jun2021
tmp.df4_full_stim_downs_jun2021_backup<- tmp.df4_full_stim_downs_jun2021

unique(tmp.df4_full_stim_downs_jun2021$timebin)

tmp_df4_timeseries_345_356_stim_downs_backup<- tmp_df4_timeseries_345_356_stim_downs

@@

tmp.df4_full_stim_downs_jun2021$ssid<- as.character(tmp.df4_full_stim_downs_jun2021$ssid)
tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)
# bind old and new data
# nrow(tmp.df4_full_stim_downs_jun2021)+ nrow(tmp_df4_timeseries_345_356_stim_downs) = 205703

tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)

tmp.df4_full_stim_downs_jun2021 <- bind_rows(tmp.df4_full_stim_downs_jun2021,tmp_df4_timeseries_345_356_stim_downs)

# tmp.df4_full_stim_downs_jun2021
table(is.na(tmp_df4_timeseries_345_356_stim_downs$pup_basCor))
# 355
table(is.na(tmp.df4_full_stim_downs_jun2021$pup_basCor))

# backup[]
tmp.df4_full_stim_downs_jun2021_60bins_backup2<- tmp.df4_full_stim_downs_jun2021_60bins

unique(db_full4new_stim_subset$ssid)

unique(tmp.df4_full_stim_downs_jun2021$ssid)
unique(db_full4new_stim_subset$ssid)

unique(tmp.df4_full_stim_downs_jun2021$tNo)
unique(db_full4new_stim_subset$tNo)

unique(tmp.df4_full_stim_downs_jun2021$trial)
unique(db_full4new_stim_subset$trial)

tmp.df4_full_stim_downs_jun2021_60bins

table(is.na(db_full4new_stim_subset$arousal))

db_full4new_stim_subset
db_full4new_stim_subset$tNo<- as.character(db_full4new_stim_subset$tNo)

# try see if arranging things solve the issue
tmp.df4_full_stim_downs_jun2021<- tmp.df4_full_stim_downs_jun2021%>%
  arrange(ssid, tNo, timerezero3)

db_full4new_stim_subset<- db_full4new_stim_subset%>%
  arrange(ssid, tNo)

db_full4new_stim_subset_valis<- subset( db_full4new_stim_subset, gaze_valid_prop>.80)

tmp.df4_full_stim_downs_jun2021_.1 <- left_join(tmp.df4_full_stim_downs_jun2021, db_full4new_stim_subset$gaze_valid_prop, by = c("ssid", "tNo", "trial"))

table(is.na(db_full4new_stim_subset_valis$gaze_valid_prop))
tmp.df4_full_stim_downs_jun2021_.1 <- left_join(db_full4new_stim_subset_valis,tmp.df4_full_stim_downs_jun2021,  by = c("ssid", "tNo", "trial"))

table(is.na(tmp.df4_full_stim_downs_jun2021_.1$arousal))
nrow(tmp.df4_full_stim_downs_jun2021_.1)
nrow(tmp.df4_full_stim_downs_jun2021)

nrow(db_full4new_stim_subset)
nrow(test)
nrow(tmp.df4_full_stim_downs_jun2021_60bins)
unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)

View(db_full4new_stim_subset)
table(is.na(db_full4new_stim_subset$arousal))
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal))

table(is.na(test$arousal))
table(is.na(test$arousal))

test1<- subset(test, is.na(arousal))

test2<- subset(test, !is.na(arousal))
table(test2$ssid)

@@

tmp.df4_full_stim_downs_jun2021_.1$Label<- substr(tmp.df4_full_stim_downs_jun2021_.1$stimIAPS, 1,8)

tmp.df4_full_stim_downs_jun2021_.1$Label2<- substr(tmp.df4_full_stim_downs_jun2021_.1$stimIAPS, 1,4)
imageJ_IAPS$Label2<- substr(imageJ_IAPS$Label, 1,4)

unique(imageJ_IAPS$Label2)
unique(tmp.df4_full_stim_downs_jun2021_.1$Label2)

# backup
tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_.1

tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_.1, imageJ_IAPS, by = "Label2")

@@

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$valence))
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$pup_basCor))

as.factor(tmp.df4_full_stim_downs_jun2021_60bins$timebin)
```

Quick check that things make sense
30 s timebins
```{r eval=FALSE, include=FALSE}
unique(tmp.df4_full_stim_downs_jun2021_with_beh$timebin2)
# group_by(stimIAPS)%>%

tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample >= 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

# higher sample rate

tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_valence2

@@

tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
  ungroup()%>%
  mutate(mediansplit_ground_valence = if_else(ValenceMean >=
                                                  median(ValenceMean,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_ground_arousal = if_else(ArousalMean >=
                                                  median(ArousalMean,
                                                         na.rm = TRUE), "High", "Low"))%>%
    mutate(mediansplit_sample_valence2 = if_else(arousal >=
                                                  median(arousal,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(valence >=
                                                  median(valence,
                                                         na.rm = TRUE), "High", "Low"))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$timebin))
ground_arousal_lab

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_ground_valence)

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2))

mediansplit_sample_arousal2

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$Group))

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(Group == "NT")%>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_sample_valence2)

@@

# i =1
# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_c))
for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

@@

timecourse_60bin_result_df %>%
  ggplot(aes(timebins, Estimate_ar_vl))+
  # geom_line(size = 1)
  # geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
  # geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
  # geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")
  #

@@

timecourse_60bin_result_df %>%
  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))

@@

tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
  # subset(ssid == 331 & tNo ==40)%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))
   ggplot(aes(timerezero3, pup_velocity))+
  geom_line()+
  geom_line(aes(y = pup_vel_smooth), color = 'red')

@@

# paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2)

@@

SCR
```{r}

db_full4new_stim_screen_pupil_nopract_nt<- subset(db_full4new_stim_screen_pupil_nopract, Group == "NT")

db_full4new_stim_screen_pupil_nopract_nt_304<- subset(db_full4new_stim_screen_pupil_nopract_nt, ssid_num>303)

db_full4new_stim_screen_pupil_nopract_nt_304

db_full4new_stim_screen_pupil_nopract_nt_304<- db_full4new_stim_screen_pupil_nopract_nt_304%>%
  ungroup%>%
  mutate(valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])%>%
  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
  mutate(TASc = scale(TAS, center = TRUE, scale = TRUE)[,1])

# models
table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.SCR))

pupil_arousal_findings$arousal_scr <- lmer(log(BIO_CDA.SCR+.1) ~ arousal_c*valence_c +
                                             (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304))

summary(pupil_arousal_findings$arousal_scr)

interactions::interact_plot(pupil_arousal_findings$arousal_scr, pred = arousal_c, modx = valence_c)

# arousal_BIO_CDA.AmpSum
pupil_arousal_findings$arousal_BIO_CDA.AmpSum <- lmer(log(BIO_CDA.AmpSum+.1) ~ arousal_c*valence_c +
                                             (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304))

summary(pupil_arousal_findings$arousal_BIO_CDA.AmpSum)

interactions::interact_plot(pupil_arousal_findings$arousal_BIO_CDA.AmpSum, pred = arousal_c, modx = valence_c)

# BIO_CDA.ISCR
pupil_arousal_findings$BIO_CDA.ISCR <- lmer(log(BIO_CDA.ISCR+.1) ~ arousal_c*valence_c +
                                             (1+valence_c|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304))

summary(pupil_arousal_findings$BIO_CDA.ISCR)

interactions::interact_plot(pupil_arousal_findings$BIO_CDA.ISCR, pred = arousal_c, modx = valence_c)

# alexithymia
table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_response))
pupil_arousal_findings$BIO_CDA.ISCR_TAS <- lmer(log(BIO_CDA.AmpSum +.1) ~ arousal_c+
                                             (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_basCor))
summary(pupil_arousal_findings$BIO_CDA.ISCR_TAS)
```

Heart rate

# keep stim and and fixation
unique(db_full6new$screencontent)
unique(db_full6new$screencontent_no)
colnames(db_full6new)

# 345:355
library(readr)
library(readr)
 # read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
View(tmp_df4_sum_full_bio_hr_self_parsed_345_356)

db_HR_bio_final_346_355_withfix <-  read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
View(db_HR_bio_final_346_355_withfix)

db_HR_bio_final_346_355_withfix$screencontent<- db_HR_bio_final_346_355_withfix$screen_content
db_HR_bio_final_346_355_withfix<- subset(db_HR_bio_final_346_355_withfix, tNo > -7)

db_HR_bio_final_346_355_withfix$screencontent_no<- if_else(db_HR_bio_final_346_355_withfix$screen_content == "fixation", 1,
                                                           if_else(db_HR_bio_final_346_355_withfix$screen_content == "stim", 2,
                                                                   if_else(db_HR_bio_final_346_355_withfix$screen_content == "valence", 3, 4)))

db_HR_bio_final_346_355_withfix_stim <- subset(db_HR_bio_final_346_355_withfix, screencontent_no<3)

# 
db_HR_bio_final_346_355_withfix_stim$tNo<- db_HR_bio_final_346_355_withfix_stim$tNo3
unique(db_HR_bio_final_346_355_withfix$tNo)
unique(db_HR_bio_final_346_355_withfix$tNo)

db_HR_bio_final_346_355_withfix_stim$tNo2<-NULL

db_HR_bio_final_346_355_withfix_stim$tNo3<- NULL

unique(db_HR_bio_final_346_355_withfix$screencontent)
unique(db_full6new_hr_fix_stim$screencontent)
# db_HR_bio_final_346_355_withfix$screencontent_no<-

colnames(db_full6new)

db_full6new_hr_fix_stim <- subset(db_full6new, screencontent_no <3)

View(db_full6new_hr_fix_stim)
# fixation"    "stim" 
colnames(db_full6new_hr_fix_stim)
colnames(db_HR_bio_final_346_355_withfix_stim)

db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR<- db_HR_bio_final_346_355_withfix_stim$Mean_HR

# keep controls
unique(db_full6new_hr_fix_stim$ssid)
db_full6new_hr_fix_stim$ssid_num <- as.numeric(as.character(db_full6new_hr_fix_stim$ssid))

db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, Group == "NT")
unique(db_full6new_hr_fix_stim_nt$ssid_num)

db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, ssid_num> 303)
unique(db_full6new_hr_fix_stim_nt$ssid)
colnames(db_full6new_hr_fix_stim_nt)
# HR differences
db_full6new_hr_fix_stim_nt$Bio_Mean_HR_fix<- if_else(db_full6new_hr_fix_stim_nt$screencontent_no ==1, db_full6new_hr_fix_stim_nt$Bio_Mean_HR, NULL)

db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix<- if_else(db_HR_bio_final_346_355_withfix_stim$screencontent_no ==1, db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR, NULL)

View(db_full6new_hr_fix_stim_nt)
View(db_HR_bio_final_346_355_withfix_stim)

db_HR_bio_final_346_355_withfix_stim$Mean_HR<- NULL

db_HR_bio_final_346_355_withfix_stim$ssid<- as.character(db_HR_bio_final_346_355_withfix_stim$ssid)

db_HR_bio_final_346_355_withfix_stim$tNo <- db_HR_bio_final_346_355_withfix_stim$tNo3.x
unique(db_HR_bio_final_346_355_withfix_stim$tNo)

db_HR_bio_final_346_355_withfix_stim$tNo <- as.character(db_HR_bio_final_346_355_withfix_stim$tNo)
db_HR_bio_final_346_355_withfix_stim$trigger <- as.character(db_HR_bio_final_346_355_withfix_stim$trigger)

db_full6new_hr_fix_stim_nt$trigger<- as.character(db_full6new_hr_fix_stim_nt$trigger)
db_full6new_hr_fix_stim_nt$trigger.x<- NULL

# db_HR_bio_final_346_355_withfix_stim$trig <- as.character(db_HR_bio_final_346_355_withfix_stim$tNo)

db_HR_bio_final_346_355_withfix_stim$triger<- NULL
db_HR_bio_final_346_355_withfix_stim$trigger.x<- NULL

db_HR_bio_final_346_355_withfix_stim$trigger.y<- NULL
db_HR_bio_final_346_355_withfix_stim$trigger2<- NULL
db_HR_bio_final_346_355_withfix_stim$trigger_200<- NULL

nrow(db_full6new_hr_fix_stim_nt)+ nrow(db_HR_bio_final_346_355_withfix_stim)
# 6895
# nrow(bind_rows(db_full6new_hr_fix_stim_nt, db_HR_bio_final_346_355_withfix_stim))
db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix
db_full6new_hr_fix_stim_nt1<- bind_rows(db_full6new_hr_fix_stim_nt,
                                        db_HR_bio_final_346_355_withfix_stim)

library(dplyr)
library(tidyverse)

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
  group_by(ssid, tNo) %>%
  arrange(ssid, tNo,screencontent_no)%>%
  fill(Bio_Mean_HR_fix, .direction = "down")%>%
  subset(screencontent_no == 2)

View(db_full6new_hr_fix_stim_nt1.1)

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(Bio_Mean_HR_dif = Bio_Mean_HR - Bio_Mean_HR_fix)

# 2 1
stim - fix

db_full6new_hr_fix_stim_nt1.1%>%
  ggplot(aes(Bio_Mean_HR_dif))+
  geom_histogram()

?scatter3d

db_full6new_hr_fix_stim_nt1.1%>%
  subset(!is.na(pup_basCor))%>%
   subset(!is.na(BIO_CDA.PhasicMax))%>%
  subset(!is.na(Bio_Mean_HR_dif))

db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt1%>%
  group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z= scale(BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])

scatter3d(x = db_full6new_hr_fix_stim_nt1$pup_basCor, 
          y = db_full6new_hr_fix_stim_nt1$BIO_CDA.PhasicMax_z, 
          z = db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, 
          fit = "smooth",

          surface = FALSE,
          point.col = "blue",
          # point
          groups = as.factor(db_full6new_hr_fix_stim_nt1$mediansplit_ground_arousal),
          ellipsoid = TRUE)

cor(db_full6new_hr_fix_stim_nt1[,c("pup_basCor", "BIO_CDA.PhasicMax_z","Bio_Mean_HR_dif")], use = "complete")

db_full6new_hr_fix_stim_nt1%>%
  group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor,BIO_CDA.PhasicMax_z, color= mediansplit_ground_valence))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ylim(0,.4)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1%>%
  # group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif))
  group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor,Bio_Mean_HR_dif_z, color= mediansplit_ground_valence))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # ylim(-7,2)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  # group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif))
  group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(BIO_CDA.PhasicMax_z,Bio_Mean_HR_dif, color= mediansplit_ground_valence))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # ylim(-7,2)+
  ggpubr::stat_cor()+
  facet_grid(~mediansplit_ground_valence)

db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif_outl <- if_else(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif)>                                                   (median(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif),na.rm = TRUE) +                                                               (4*(sd(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif), na.rm = TRUE)))), "outlier", "not outlier")

db_full6new_hr_fix_stim_nt1.1%>%
  ggplot(aes(Bio_Mean_HR_dif))+
  geom_histogram()+
  facet_grid(~Bio_Mean_HR_dif_outl)

```{r}
db_full6new_hr_fix_stim_nt1.1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(ssid_num<500)%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif_ssid = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_stim = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS, Bio_Mean_HR_dif))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()
